Exploring the Pareto front of multi-objective COVID-19 mitigation policies using reinforcement learning

### 2023-02-02 paper/main.tex
processed pieters comments (up to 3.2)

\subsection{Multi-Objective Metrics}
Comparing the learned coverage sets of different algorithms is a non-trivial task, as one algorithm's output might dominate the other in some region of the objective-space, but be dominated in another. Intuitively, one would generally prefer the algorithm that covers a wider range of decision maker preferences. In this work we use several metrics to evaluate our algorithm's performance.

A widely used metric in the literature is called the \emph{hypervolume}~\cite{zitzler2003}. This metric evaluates the learned coverage set by computing its volume with respect to a fixed specified reference point. This metric is, by definition, the highest for the Pareto front, as no other possible solution can increase its volume (since they are all dominated). One disadvantage of the hypervolume is that it can be difficult to interpret. For example, when working in high-dimensional objective-spaces, adding or removing a single point can lead to wildly different hypervolume values, especially if the point lies close to an extremum of the space.

To alleviate these shortcomings, we additionally evaluate our work on a different metric called the $\varepsilon$-indicator $I_\varepsilon$~\cite{zitzler2003}, which measures how close a coverage set is to the Pareto front $\mathcal{F}$. Intuitively, $I_\varepsilon$ shows that any solution of $\mathcal{F}$ is \emph{at most} $\varepsilon$ better with respect to each objective $o$ than the closest solution of the evaluated coverage set:

\begin{equation}
\label{eq:epsilon-metric}
    I_{\varepsilon} = 
    \inf_{\varepsilon\in\mathbb{R}} 
    \{ 
    \forall\ \momdpvaluefunction^\pi\!{\in}\ \mathcal{F}, ~
    \exists\ \momdpvaluefunction^{\pi'}\!{\in}\ \hat{\Pi} :\ 
    || \mdpvaluefunction^\pi - \mdpvaluefunction_o^{\pi'} ||_{\infty} \le \varepsilon
    \}
\end{equation}

@@

We note that the $\varepsilon$-indicator metric is quite pessimistic, as it measures worst-case performance~\cite{zintgraf2015}, e.g., it will still report bad performance as long as a single point of the Pareto front is not correctly modeled, even if all the other points are covered. As such, we also use the $I_{\varepsilon-mean}$ \cite{reymond2022pcn} which measures the \emph{average} $\varepsilon$ distance of the solutions in $\mathcal{F}$ with respect to the evaluated coverage set.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{COVID-19 model and the \momdpname\  MOMDP}
\label{sec:sars-cov2-momdp}
\subsection{Stochastic compartment model for SARS-CoV-2}
\label{sec:sars-cov2-momdp_model}
As an environment to evaluate non-pharmaceutical interventions, we consider the adapted version of the SEIR compartmental model presented by Abrams et al., that was used to investigate exit strategies in Belgium after the first epidemic wave of SARS-CoV-2~\cite{abrams2021modelling}. This model constitutes a discrete-time stochastic model, that considers an age-structured population. This model generalises a standard SEIR model\footnote{A standard SEIR model divides the population into four different states, i.e., susceptible, exposed, infectious and recovered individuals.}, extended to capture the different stages of disease spread and history that are associated with SARS-CoV-2 (i.e., pre-symptomatic, asymptomatic, symptomatic with mild symptoms and symptomatic with severe symptoms) and to represent the stages associated with severe disease, i.e., hospitalisation, admission to the intensive care unit (ICU) and death. 
As we consider an age-structured population, we consider this extended SEIR structure for $\agegroups = 10$ age groups,  i.e., $[0-10), [10-20), [20-30), [30-40), [40-50), [50-60), [60-70), [70-80), [80-90), [90,\infty)$. Contacts of the different age-groups which impact the propagation rate of the epidemic are modeled using social contact matrices (SCMs). We define a SCM for 6 different social environments: $\chome, \cwork, \ctransport, \cschool, \cleisure, \cother$ for the home, work, transport, school, leisure, other environments respectively.
The model is described by a set of ordinary differential equations (ODEs), as described in SI.
By formulating this set of differential equations defined above as a chain-binomial process we can obtain stochastic trajectories from this model~\cite{abrams2021modelling}.

>>>>

\subsection{Multi-Objective Metrics}
Comparing the learned coverage sets produced by different algorithms is a non-trivial task, as one algorithm's output might dominate the other in some region of the objective-space, but be dominated in another. Intuitively, one would generally prefer the algorithm that covers a wider range of decision maker preferences. In this work we use several metrics to evaluate our algorithm's performance.

A widely used metric in the literature is called the \emph{hypervolume}~\cite{zitzler2003}. This metric evaluates the learned coverage set by computing its volume with respect to a fixed specified reference point. The reference point is taken as a lower bound on the achievable returns so that the volumes are always positive. By definition, the solutions contained in the Pareto front dominate all other possible solutions. Thus, no other solution can further increase the volume under the Pareto front. This means that the hypervolume is the highest for the Pareto front. One disadvantage of the hypervolume is that it can be difficult to interpret. For example, when working in high-dimensional objective-spaces, adding or removing a single point can drastically change hypervolume values, especially if the point lies close to an extremum of said space.

To counterpoise these shortcomings, we additionally evaluate our work on a different metric called the $\varepsilon$-indicator $I_\varepsilon$~\cite{zitzler2003}, which measures how close a coverage set is to the Pareto front $\mathcal{F}$. Intuitively, $I_\varepsilon$ shows that any solution of $\mathcal{F}$ is \emph{at most} $\varepsilon$ better with respect to each objective $o$ than the closest solution of the evaluated coverage set:

\begin{equation}
\label{eq:epsilon-metric}
    I_{\varepsilon} = 
    \inf_{\varepsilon\in\mathbb{R}} 
    \{ 
    \forall\ \momdpvaluefunction^\pi\!{\in}\ \mathcal{F}, ~
    \exists\ \momdpvaluefunction^{\pi'}\!{\in}\ \hat{\Pi} :\ 
    || \momdpvaluefunction^\pi - \momdpvaluefunction^{\pi'} ||_{\infty} \le \varepsilon
    \},
\end{equation}
%
where $||.||_{\infty}$, the L-infinity norm, returns the magnitude of the largest entry of a vector.

@@

We note that the $\varepsilon$-indicator metric is quite pessimistic, as it measures worst-case performance~\cite{zintgraf2015}, i.e., e.g., it will still report bad performance as long as a single point of the Pareto front is not correctly modeled, even if all the other points are covered. As such, we also use the $I_{\varepsilon-mean}$ \cite{reymond2022pcn} which measures the \emph{average} $\varepsilon$ distance of the solutions in $\mathcal{F}$ with respect to the evaluated coverage set.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{COVID-19 model and the \momdpname\  MOMDP}
\label{sec:sars-cov2-momdp}
\subsection{Stochastic compartment model for SARS-CoV-2}
\label{sec:sars-cov2-momdp_model}
As an environment to evaluate non-pharmaceutical interventions, we consider the adapted version of the SEIR compartmental model presented by Abrams et al., that was used to investigate exit strategies in Belgium after the first epidemic wave of SARS-CoV-2~\cite{abrams2021modelling}. This model constitutes a discrete-time stochastic model, that considers an age-structured population. This model generalises a standard SEIR model\footnote{A standard SEIR model divides the population into four different states, i.e., susceptible, exposed, infectious and recovered individuals.}, extended to capture the different stages of disease spread and history that are associated with SARS-CoV-2 (i.e., pre-symptomatic, asymptomatic, symptomatic with mild symptoms and symptomatic with severe symptoms) and to represent the stages associated with severe disease, i.e., hospitalisation, admission to the intensive care unit (ICU) and death. 
As we consider an age-structured population, we consider this extended SEIR structure for $\agegroups = 10$ age groups,  i.e., $[0-10), [10-20), [20-30), [30-40), [40-50), [50-60), [60-70), [70-80), [80-90), [90,100+)$. Contacts of the different age-groups, which impact the propagation rate of the epidemic, are modeled using social contact matrices (SCMs). We define a SCM for 6 different social environments: $\chome, \cwork, \ctransport, \cschool, \cleisure, \cother$ for the home, work, transport, school, leisure, other environments respectively.
The model is described by a set of ordinary differential equations (ODEs), as described in SI.
By formulating this set of differential equations a chain-binomial process (as detailed in SI) we can obtain stochastic trajectories from this model~\cite{abrams2021modelling}.
